---
format:
  typst:
    font-size: 10pt
    margin:
      top: 0.6in
      bottom: 0.6in
      left: 0.75in
      right: 0.75in
    include-in-header: cv-template.typ
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
options(device = pdf)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(glue)
library(knitr)
knitr::opts_chunk$set(dev = "pdf")

truncate_authors <- function(authors, max_authors = 6, self = "Timothy Keyes") {
  parts <- str_split(authors, ",\\s*")[[1]]
  if (length(parts) <= max_authors) return(authors)
  self_idx <- which(str_detect(parts, fixed(self)))
  keep <- parts[1:max_authors]
  if (length(self_idx) > 0 && self_idx[1] > max_authors) {
    keep[max_authors] <- parts[self_idx[1]]
  }
  paste0(paste(keep, collapse = ", "), ", et al.")
}
```

# Timothy Keyes — Curriculum Vitae

tkeyes\@stanford.edu · [keyes-timothy.github.io](https://keyes-timothy.github.io) · [GitHub](https://github.com/keyes-timothy) · [Google Scholar](https://scholar.google.com/citations?user=ZzAOZ1QAAAAJ&hl=en) · [LinkedIn](https://www.linkedin.com/in/timothy-keyes/)

## Education

```{r}
#| label: education
#| results: asis
education <- read_csv("data/cv_education.csv", show_col_types = FALSE)

for (i in seq_len(nrow(education))) {
  row <- education[i, ]
  cat(glue("**{row$degree}** — {row$institution}, {row$location} (*{row$status}*)"), "\n\n")
  if (!is.na(row$details) && nchar(trimws(row$details)) > 0) {
    parts <-
      str_split(row$details, ";\\s*")[[1]] |>
      trimws()
    parts <- parts[nchar(parts) > 0]
    for (p in parts) {
      cat(glue("- {p}"), "\n")
    }
    cat("\n")
  }
}
```

## Experience

```{r}
#| label: experience
#| results: asis
experience <- read_csv("data/cv_experience.csv", show_col_types = FALSE)

for (i in seq_len(nrow(experience))) {
  row <- experience[i, ]
  cat(glue("**{row$title}** — {row$organization}, {row$location} (*{row$status}*)"), "\n\n")
  if (!is.na(row$details) && nchar(trimws(row$details)) > 0) {
    parts <-
      str_split(row$details, ";\\s*")[[1]] |>
      trimws()
    parts <- parts[nchar(parts) > 0]
    for (p in parts) {
      cat(glue("- {p}"), "\n")
    }
    cat("\n")
  }
}
```

## Publications

†Co-first author · ‡Co-second author

```{r}
#| label: publications
#| results: asis
pubs <-
  read_csv("data/publications.csv", show_col_types = FALSE) |>
  mutate(
    across(where(is.character), \(.x) replace_na(.x, "")),
    year = suppressWarnings(as.integer(year)),
    co_author_count = suppressWarnings(as.integer(co_author_count)),
    co_author_start = suppressWarnings(as.integer(co_author_start)),
    position_rank = case_when(
      author_position %in% c("first", "co_first") ~ 1L,
      author_position %in% c("second", "co_second") ~ 2L,
      TRUE ~ 3L
    )
  ) |>
  arrange(desc(year), position_rank, authors)

years <- unique(pubs$year)

for (yr in years) {
  cat("\n### ", yr, "\n\n", sep = "")

  yr_pubs <-
    pubs |>
    filter(year == yr)

  for (j in seq_len(nrow(yr_pubs))) {
    row <- yr_pubs[j, ]
    authors <- row$authors
    marker <- ""
    n_marked <- 0L

    if (!is.na(row$author_position) && row$author_position == "co_first") {
      marker <- "\u2020"
      n_marked <- if (!is.na(row$co_author_count) && row$co_author_count > 0) as.integer(row$co_author_count) else 2L
    } else if (!is.na(row$author_position) && row$author_position == "co_second") {
      marker <- "\u2021"
      n_marked <- if (!is.na(row$co_author_count) && row$co_author_count > 0) as.integer(row$co_author_count) else 2L
    }

    start_pos <- if (!is.na(row$co_author_start) && row$co_author_start > 0) as.integer(row$co_author_start) else 1L

    if (nchar(marker) > 0 && n_marked > 0) {
      author_parts <- str_split(authors, ",\\s*")[[1]]
      end_pos <- min(start_pos + n_marked - 1L, length(author_parts))
      for (k in start_pos:end_pos) {
        author_parts[k] <- paste0(author_parts[k], marker)
      }
      authors <- paste(author_parts, collapse = ", ")
    }

    authors <- truncate_authors(authors)
    authors <- str_replace_all(authors, "Timothy Keyes", "**Timothy Keyes**")

    cat(glue("- {authors}. {row$title}. *{row$journal}*."), "\n")
  }
  cat("\n")
}
```

## Awards & Honors

```{r}
#| label: awards
#| results: asis
awards <-
  read_csv("data/cv_awards.csv", show_col_types = FALSE) |>
  mutate(sort_year = as.integer(str_extract(year, "\\d{4}"))) |>
  arrange(desc(sort_year)) |>
  select(-sort_year)

for (i in seq_len(nrow(awards))) {
  row <- awards[i, ]
  cat(glue("- **{row$award}**, {row$organization} ({row$year})"), "\n")
}
```

## Media & Press

```{r}
#| label: media
#| results: asis
media <-
  read_csv("data/cv_media.csv", show_col_types = FALSE) |>
  mutate(across(where(is.character), \(.x) replace_na(.x, ""))) |>
  arrange(desc(year))

for (i in seq_len(nrow(media))) {
  row <- media[i, ]
  cat(glue("- **{row$title}** — {row$type}, {row$outlet} ({row$year})"), "\n")
}
```

## Selected Talks

```{r}
#| label: talks
#| results: asis
talks <-
  read_csv("data/talks.csv", show_col_types = FALSE) |>
  mutate(across(where(is.character), \(.x) replace_na(.x, ""))) |>
  arrange(desc(as.Date(date)))

for (i in seq_len(nrow(talks))) {
  row <- talks[i, ]
  cat(glue("- **{row$title}**. {row$venue}, {row$location}."), "\n")
}
```

## Skills

**Clinical AI & LLM Systems:** EHR-integrated AI, agentic workflow design, LLM evaluation, RAG, clinical summarization, post-deployment monitoring

**Machine Learning & Statistics:** Supervised learning, calibration, bootstrap inference, survival analysis, clustering, gradient boosting, deep learning, tabPFN

**Healthcare Data & Governance:** Epic EHR data, FHIR, clinical workflow integration, AI governance, model lifecycle management, clinical operations analytics

**Programming & Data Science:** Python, R, SQL, Bash, pandas, scikit-learn, XGBoost, PyTorch, tidyverse, tidymodels, Bioconductor, Shiny

**Platforms & Tools:** Databricks, Azure OpenAI, LiteLLM, FastAPI, Pydantic, Git, Docker, Epic, MCP, Quarto

**Biomedical Domains:** Clinical ML, LLMs in health care, single-cell analysis, mass cytometry, computational cancer biology, pediatric leukemia