---
title: "Timothy Keyes"
subtitle: "Curriculum Vitae"
format:
  typst:
    font-size: 10pt
    margin:
      top: 0.75in
      bottom: 0.75in
      left: 0.75in
      right: 0.75in
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
options(bitmapType = "cairo")
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(glue)
library(knitr)
knitr::opts_chunk$set(dev = "png", fig.width = 6, fig.height = 4)
```

tkeyes\@stanford.edu · [keyes-timothy.github.io](https://keyes-timothy.github.io) · [GitHub](https://github.com/keyes-timothy) · [Google Scholar](https://scholar.google.com/citations?user=ZzAOZ1QAAAAJ&hl=en) · [LinkedIn](https://www.linkedin.com/in/timothy-keyes/)

## Education

```{r}
#| label: education
#| results: asis
education <- read_csv("data/cv_education.csv", show_col_types = FALSE)

education |>
  pmap_chr(function(degree, institution, location, status, details) {
    detail_line <- if (!is.na(details) && nchar(trimws(details)) > 0) {
      parts <- str_split(details, ";\\s*")[[1]] |> trimws()
      parts <- parts[nchar(parts) > 0]
      paste0("\n    - ", paste(parts, collapse = "\n    - "))
    } else {
      ""
    }
    glue("**{degree}** | {institution}, {location} | *{status}*{detail_line}")
  }) |>
  paste(collapse = "\n\n") |>
  cat()
```

## Experience

```{r}
#| label: experience
#| results: asis
experience <- read_csv("data/cv_experience.csv", show_col_types = FALSE)

experience |>
  pmap_chr(function(title, organization, location, status, details) {
    detail_line <- if (!is.na(details) && nchar(trimws(details)) > 0) {
      parts <- str_split(details, ";\\s*")[[1]] |> trimws()
      parts <- parts[nchar(parts) > 0]
      paste0("\n    - ", paste(parts, collapse = "\n    - "))
    } else {
      ""
    }
    glue("**{title}** | {organization}, {location} | *{status}*{detail_line}")
  }) |>
  paste(collapse = "\n\n") |>
  cat()
```

## Publications

```{r}
#| label: publications
#| results: asis
pubs <- read_csv("data/publications.csv", show_col_types = FALSE) |>
  mutate(
    across(where(is.character), \(.x) replace_na(.x, "")),
    year = suppressWarnings(as.integer(year)),
    co_author_count = suppressWarnings(as.integer(co_author_count)),
    co_author_start = suppressWarnings(as.integer(co_author_start)),
    position_rank = case_when(
      author_position %in% c("first", "co_first") ~ 1L,
      author_position %in% c("second", "co_second") ~ 2L,
      TRUE ~ 3L
    )
  ) |>
  arrange(desc(year), position_rank, authors)

pubs |>
  pmap_chr(function(year, authors, journal, title, abstract, citation, link,
                    file_name, preferred, author_position, co_author_count,
                    co_author_start, position_rank, topic) {
    # Apply co-authorship markers
    marker <- ""
    n_marked <- 0L
    if (!is.na(author_position) && author_position == "co_first") {
      marker <- "\u2020"
      n_marked <- if (!is.na(co_author_count) && co_author_count > 0) as.integer(co_author_count) else 2L
    } else if (!is.na(author_position) && author_position == "co_second") {
      marker <- "\u2021"
      n_marked <- if (!is.na(co_author_count) && co_author_count > 0) as.integer(co_author_count) else 2L
    }

    start_pos <- if (!is.na(co_author_start) && co_author_start > 0) as.integer(co_author_start) else 1L

    if (nchar(marker) > 0 && n_marked > 0) {
      author_parts <- str_split(authors, ",\\s*")[[1]]
      end_pos <- min(start_pos + n_marked - 1L, length(author_parts))
      for (i in start_pos:end_pos) {
        author_parts[i] <- paste0(author_parts[i], marker)
      }
      authors_display <- paste(author_parts, collapse = ", ")
    } else {
      authors_display <- authors
    }

    # Bold Timothy Keyes
    authors_display <- str_replace_all(authors_display, "Timothy Keyes", "**Timothy Keyes**")

    glue("{authors_display}. {title}. *{journal}* ({year}).")
  }) |>
  paste0("- ", x = _) |>
  paste(collapse = "\n") |>
  cat()
```

## Awards & Honors

```{r}
#| label: awards
#| results: asis
awards <- read_csv("data/cv_awards.csv", show_col_types = FALSE) |>
  mutate(sort_year = as.integer(str_extract(year, "\\d{4}"))) |>
  arrange(desc(sort_year)) |>
  select(-sort_year)

awards |>
  pmap_chr(function(award, organization, year, details) {
    glue("- **{award}**, {organization} ({year})")
  }) |>
  paste(collapse = "\n") |>
  cat()
```

## Media & Press

```{r}
#| label: media
#| results: asis
media <- read_csv("data/cv_media.csv", show_col_types = FALSE) |>
  mutate(across(where(is.character), \(.x) replace_na(.x, ""))) |>
  arrange(desc(year))

media |>
  pmap_chr(function(year, type, outlet, title, link) {
    glue("- {title}. {type} --- {outlet} ({year})")
  }) |>
  paste(collapse = "\n") |>
  cat()
```

## Skills

**Clinical AI & LLM Systems**: EHR-integrated AI applications, agentic and multi-agent workflow design, LLM evaluation, retrieval-augmented generation (RAG), clinical summarization, post-deployment monitoring

**Machine Learning & Statistics**: supervised learning, calibration, bootstrap inference, survival analysis, class imbalance adjustment, clustering, gradient boosting, deep learning, tabular foundation models (tabPFN)

**Healthcare Data & Governance**: Epic EHR data, FHIR, clinical workflow integration, AI governance, model lifecycle management, clinical operations analytics, human-in-the-loop workflow design

**Programming & Data Science**: Python, R, SQL, Bash, pandas, scikit-learn, XGBoost, PyTorch, tidyverse, tidymodels, Bioconductor, Shiny

**Platforms & Tools**: Databricks, Azure OpenAI, LiteLLM, FastAPI, Pydantic, Git, Docker, Epic, MCP, Quarto

**Biomedical Domains**: clinical machine learning, LLMs in health care, single-cell analysis, mass cytometry, computational cancer biology, pediatric leukemia