---
title: "CV"
toc: true
---

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

# ---- Load required packages ----
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(glue)
```

```{r}
#| label: cv-helpers
#| echo: false

# ---- Helper: check if a string has meaningful content ----
has_text_cv <- function(x) {
  !is.na(x) && nchar(trimws(x)) > 0
}

#' Render a timeline-style CV entry (education or experience)
#'
#' Produces an HTML div with a colored left border, showing the degree/title,
#' institution, location, year range, and optional details.
#'
#' @param main Character. Primary label (e.g. degree or job title).
#' @param sub Character. Secondary label (e.g. institution name).
#' @param location Character. City/state.
#' @param years Character. Formatted year range string.
#' @param details Character. Optional additional details.
#' @return HTML string for a single timeline entry.
render_entry <- function(main, sub, location, years, details = "") {
  # Only show the details div if there's actual content

  details_html <- if (!is.na(details) && nchar(trimws(details)) > 0) {
    # Split on semicolons and render each part as a separate line
    parts <- str_split(details, ";\\s*")[[1]]
    parts <- trimws(parts)
    parts <- parts[nchar(parts) > 0]
    lines <- paste(parts, collapse = "<br>")
    glue("<div class='cv-details'>{lines}</div>")
  } else {
    ""
  }

  glue(
    "<div class='cv-entry'>",
    "<div class='cv-entry-header'>",
    "<strong>{main}</strong>",
    "<span class='cv-years'>{years}</span>",
    "</div>",
    "<div class='cv-entry-sub-row'>",
    "<span class='cv-entry-sub'>{sub}</span>",
    "<span class='cv-location'>{location}</span>",
    "</div>",
    "{details_html}",
    "</div>"
  )
}

#' Render a compact award/honor entry
#'
#' @param award Character. Award name.
#' @param organization Character. Granting organization.
#' @param year Character. Year awarded.
#' @param details Character. Optional description.
#' @return HTML string for a single award entry.
render_award <- function(award, organization, year, details = "") {
  # If details exist, wrap in a clickable <details>/<summary> element;
  # otherwise, render a simple non-interactive line.
  has_details <- !is.na(details) && nchar(trimws(details)) > 0

  if (has_details) {
    glue(
      "<details class='cv-award'>",
      "<summary class='cv-award-summary'>",
      "<span class='cv-award-title'>{award}</span>",
      "<span class='cv-award-org-inline'>{organization}</span>",
      "<span class='cv-years'>{year}</span>",
      "</summary>",
      "<div class='cv-award-details'>{details}</div>",
      "</details>"
    )
  } else {
    glue(
      "<div class='cv-award'>",
      "<div class='cv-award-summary'>",
      "<span class='cv-award-title'>{award}</span>",
      "<span class='cv-award-org-inline'>{organization}</span>",
      "<span class='cv-years'>{year}</span>",
      "</div>",
      "</div>"
    )
  }
}
```

## Education

```{r}
#| label: education
#| echo: false
#| results: asis

# ---- Read and render education entries ----
# Source: data/cv_education.csv (degree, institution, location, years, details)
education <- read_csv("data/cv_education.csv", show_col_types = FALSE)

education |>
  pmap_chr(
    function(degree, institution, location, status, details) {
      render_entry(degree, institution, location, status, details)
    }
  ) |>
  walk(\(.html) cat(.html, "\n\n"))
```

## Experience

```{r}
#| label: experience
#| echo: false
#| results: asis

# ---- Read and render work experience entries ----
# Source: data/cv_experience.csv
experience <- read_csv("data/cv_experience.csv", show_col_types = FALSE)

experience |>
  pmap_chr(
    function(title, organization, location, status, details) {
      render_entry(title, organization, location, status, details)
    }
  ) |>
  walk(\(.html) cat(.html, "\n\n"))
```

## Selected Publications

```{r}
#| label: cv-publications
#| echo: false
#| results: asis

# ---- Read publication data and render selected publications ----
# Uses the same CSV as the Publications page, filtered to preferred == TRUE.
# Includes co-authorship markers (dagger/double-dagger) and name bolding.
pubs <-
  read_csv("data/publications.csv", show_col_types = FALSE) |>
  mutate(
    across(where(is.character), \(.x) replace_na(.x, "")),
    preferred = str_to_lower(as.character(preferred)) %in%
      c("true", "t", "1", "yes", "y"),
    year = suppressWarnings(as.integer(year)),
    co_author_count = suppressWarnings(as.integer(co_author_count)),
    co_author_start = suppressWarnings(as.integer(co_author_start)),
    # Sorting rank: first/co-first = 1, co-second = 2, middle = 3
    position_rank = case_when(
      author_position %in% c("first", "co_first") ~ 1L,
      author_position %in% c("second", "co_second") ~ 2L,
      TRUE ~ 3L
    )
  ) |>
  filter(preferred) |>
  arrange(desc(year), position_rank, authors)

pubs |>
  pmap_chr(
    function(
      year, authors, journal, title, abstract, citation, link,
      file_name, preferred, author_position, co_author_count,
      co_author_start, position_rank, topic
    ) {
      # ---- Apply co-authorship markers to author names ----
      marker <- ""
      n_marked <- 0L

      if (has_text_cv(author_position) && author_position == "co_first") {
        marker <- "\u2020"
        n_marked <- if (!is.na(co_author_count) && co_author_count > 0) {
          as.integer(co_author_count)
        } else {
          2L
        }
      } else if (has_text_cv(author_position) && author_position == "co_second") {
        marker <- "\u2021"
        n_marked <- if (!is.na(co_author_count) && co_author_count > 0) {
          as.integer(co_author_count)
        } else {
          2L
        }
      }

      start_pos <- if (!is.na(co_author_start) && co_author_start > 0) {
        as.integer(co_author_start)
      } else {
        1L
      }

      if (nchar(marker) > 0 && n_marked > 0) {
        author_parts <- str_split(authors, ",\\s*")[[1]]
        end_pos <- min(start_pos + n_marked - 1L, length(author_parts))
        for (i in start_pos:end_pos) {
          author_parts[i] <- paste0(author_parts[i], marker)
        }
        authors_display <- paste(author_parts, collapse = ", ")
      } else {
        authors_display <- authors
      }

      # Bold "Timothy Keyes" in the display string
      authors_display <- str_replace_all(
        authors_display,
        "Timothy Keyes",
        "<strong>Timothy Keyes</strong>"
      )

      # Build linked title
      title_html <- if (has_text_cv(link)) {
        glue("<a href='{link}' target='_blank'>{title}</a>")
      } else {
        title
      }

      # Assemble compact publication entry
      glue(
        "<div class='cv-pub'>",
        "<div class='cv-pub-title'>{title_html}</div>",
        "<div class='cv-pub-meta'>",
        "{authors_display}. <em>{journal}</em> ({year}).",
        "</div>",
        "</div>"
      )
    }
  ) |>
  walk(\(.html) cat(.html, "\n\n"))
```

<p style="margin-top: 0.5rem;">
<a href="publications.html">&rarr; View full publication list</a>
</p>

## Awards & Honors

```{r}
#| label: awards
#| echo: false
#| results: asis

# ---- Read and render awards ----
# Source: data/cv_awards.csv
awards <- read_csv("data/cv_awards.csv", show_col_types = FALSE) |>
  mutate(sort_year = as.integer(str_extract(year, "\\d{4}"))) |>
  arrange(desc(sort_year)) |>
  select(-sort_year)

awards |>
  pmap_chr(
    function(award, organization, year, details) {
      render_award(award, organization, year, details)
    }
  ) |>
  walk(\(.html) cat(.html, "\n\n"))
```

## Media & Press

```{r}
#| label: media
#| echo: false
#| results: asis

# ---- Read and render media/press entries ----
# Source: data/cv_media.csv (year, type, outlet, title, link)
media <-
  read_csv("data/cv_media.csv", show_col_types = FALSE) |>
  mutate(across(where(is.character), \(.x) replace_na(.x, ""))) |>
  arrange(desc(year))

media |>
  pmap_chr(
    function(year, type, outlet, title, link) {
      # Link the title if a URL is available
      title_html <- if (has_text_cv(link)) {
        glue("<a href='{link}' target='_blank'>{title}</a>")
      } else {
        title
      }

      glue(
        "<div class='cv-award'>",
        "<div class='cv-award-header'>",
        "<strong>{title_html}</strong>",
        "</div>",
        "<div class='cv-award-org'>{type} \u2014 {outlet} ({year})</div>",
        "</div>"
      )
    }
  ) |>
  walk(\(.html) cat(.html, "\n\n"))
```

## Skills

**Clinical AI & LLM Systems**: EHR-integrated AI applications, agentic and multi-agent workflow design, LLM evaluation, retrieval-augmented generation (RAG), clinical summarization, post-deployment monitoring

**Machine Learning & Statistics**: supervised learning, calibration, bootstrap inference, survival analysis, class imbalance adjustment, clustering, gradient boosting, deep learning, tabular foundation models (tabPFN)

**Healthcare Data & Governance**: Epic EHR data, FHIR, clinical workflow integration, AI governance, model lifecycle management, clinical operations analytics, human-in-the-loop workflow design

**Programming & Data Science**: Python, R, SQL, Bash, pandas, scikit-learn, XGBoost, PyTorch, tidyverse, tidymodels, Bioconductor, Shiny, Quarto

**Platforms & Tools**: Databricks, Azure OpenAI, LiteLLM, FastAPI, Pydantic, Git, Docker, Epic, MCP

**Biomedical Domains**: clinical machine learning, LLMs in health care, single-cell analysis, mass cytometry, computational cancer biology, pediatric leukemia